---
title: "Homework I - Solution"
author: "Gul Inan"
date: "10/29/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Answer

- **Answer 1:**

- Load the `tidyverse` library first. We will need it throughout the homework.

```{r, warning=F, message=F}
library(tidyverse)
```

- Read in the data into R and check it:

```{r}
#i could not import csv file, and i
#got help from here: https://stackoverflow.com/a/45977065
library(readxl)
music_revenue <- read_excel("data/Revenue_Chart_Full_Data.xlsx", skip = 1) 
```

- See a portion of the data:

```{r}
music_revenue %>% 
  head(5)
```

- Check the structure of the data:

```{r}
str(music_revenue)
```

- **Answer 2:**

```{r}
revenue_18_20 <- music_revenue %>% 
                 select("Year"="Year (copy)", "Format", "Value"="Value (Actual)") %>% 
                 filter(Year >= 2018) %>%
                 arrange(Year) %>% 
                 mutate(Value = as.numeric(Value))
```

- A portion of the data:

```{r}
revenue_18_20 %>% 
              head(10)
```
 
- The structure of the data:

```{r}
revenue_18_20 %>% 
  str()
```

- Get the summary statistics:

```{r}
annual_retail <- revenue_18_20 %>% 
                 group_by(Year) %>% 
                  summarize(tol_revenue = sum(Value)) 
```

```{r}
annual_retail %>% 
              print()
```


- **Answer 3:**

```{r, eval=F}
streaming <- c("Paid Subscription", "On-Demand Streaming (Ad-Supported)", "Other Ad-Supported Streaming", 
"SoundExchange Distributions", "Limited Tier Paid Subscription")

stream_20 <- revenue_18_20 %>% 
             filter(Year == 2020) %>% 
             filter(Format %in% streaming) %>% 
             select(Value) %>% 
             summarize(total_stream = sum(Value))
```


```{r, eval=F}
stream_20  %>% 
           View()
```

- **Answer 4:**

```{r}
#define some character vectors to increase code readability.
stream <- c("Paid Subscription", "On-Demand Streaming (Ad-Supported)", "Other Ad-Supported Streaming", "SoundExchange Distributions", "Limited Tier Paid Subscription")
physical <- c("LP/EP", "CD")
download <- c("Download Album", "Download Single")
```

```{r}
revenue_categorized_20 <- revenue_18_20 %>% 
                          filter(Year == 2020) %>% 
                          mutate(category = case_when( Format %in% stream ~ "Streaming",
                               Format == "Synchronization" ~ "Synchronization",
                               Format %in% physical ~ "Physical",
                               Format %in% download ~ "Digital Downloads",
                               TRUE ~ "The Others"
    
  ))
```

- View the new data

```{r, eval=F}
View(revenue_categorized_20)
```

- Calculate the percentage of each category share:

```{r}
share_table   <- revenue_categorized_20 %>%
                 group_by(category) %>%
                 summarize(cat_total=sum(Value)) %>% 
                 mutate(prop = round(cat_total /sum(cat_total) * 100,2))
```

- View the data.

```{r, eval=F}
share_table %>% 
  View()
```

- Get the table.


```{r}
share_table %>% 
  print()
```


- **Answer 5:**

- Reproduce Figure 5. It is a stacked bar chart. We need to convert Year and Format into character variables.


```{r}
fig_5_data <- revenue_18_20 %>%
              filter(Format %in% c("SoundExchange Distributions", "Other Ad-Supported Streaming")) %>% 
mutate_at(vars("Year", "Format"), as.character)
```

```{r, eval=F}
fig_5_data %>% 
  View()
```

```{r}
str(fig_5_data)
```

- Generate the Figure.

```{r}
library(ggplot2)
```

```{r}
labels <- c("$ 1,161", "$1,115", "$1,1559")
```



```{r}
fig_5_data %>% 
ggplot(aes(x=Year, y=Value, fill=Format)) + 
  geom_col(position="stack") +
  scale_fill_manual(values = c("#c5db84","#347b7b")) +
  scale_y_continuous(expand = c(0,0)) +
  ggtitle("U.S. DIGITAL AND CUSTOMIZED \n RADIO REVENUES", subtitle = "Source: RIAA" ) +
  labs("y" = "$ MILLIONS") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"),
        plot.subtitle =  element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.line.x  = element_line(size = 0.6),
        axis.line.y  = element_blank(),
        axis.text.y  = element_blank(),
        axis.ticks.y = element_blank(),
        legend.title = element_blank(),
        legend.position = "bottom")
#geom_text(aes(label = labels, y = c(208.17685,208.17685,208.17685)), size = 3)
```





